Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-11-26 Ben_Manuscripts/stochastic_transport/Draft.tex
Edits

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories, in order
  to predict solute mean squared displacements (MSDs). With our first model, based
  on the anomalous diffusion literature, we show how solute dynamics can be modeled as
  a fractional diffusion process subordinate to a continuous time random walk.
  We parameterize the distribution of dwell times, hop lengths between dwells and
  correlation between hops. We explore 2 variations of the model. The first variation
  applies a single set of parameters to the solutes and the second applies 2 sets
  of parameters based on the solute's radial distance from the closest pore center.
  Our second model, an adaptation of Markov state models, treats the configurational
  state of the system as a Markov process, each of which has state dependent 
  transport behavior. For each state and transition between states, we parameterized
  the distribution and temporal correlation structure of positional fluctuations as
  a means of characterization and to allow us to predict solute MSDs.
  We show that our models reasonably reproduce MSDs calculated from molecular 
  simulations. The anomalous diffusion model shows superior predictive performance, 
  in many cases reproducing MD results well within error. Finally, we use the 
  parameters of each model to identify specific differences in solute transport
  behavior which can help suggest modifications that can be made to LLC membrane 
  monomers in order to increase or reduce selectivity towards a specific solute
  or class of solutes.

@@

  Mathematical descriptions of transport in complex separations membranes are 
  a powerful way to understand mechanisms and formulate membrane design principles. 
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  The complexity of a model generally parallels the complexity of the transport 
  mechanism at hand, as well as the transport information the model conveys.
  In dense homogeneous membranes, the solution-diffusion model can extract 
  diffusion and partition coefficients and has successfully predicted solute 
  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
  models yield predictions of diffusion coefficients and solute transport rates 
  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
  tracking approaches take us beyond continuum modeling and allow us to 
  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
  level, one can use molecular dynamics (MD) simulations to study both single 
  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
  All of these approaches facilitate speculation on the molecular origins of separations
  by attempting to give a more intuitive understanding of how solutes move as a function
  of their environment, in turn suggesting experiments that could be performed.

@@

  %BJC4: Added next two paragraphs to help ease more into time series modeling
  So far, our molecular models have provided valuable qualitative mechanistic insight 
  with some quantitative support which already allows us to speculate about new LLC
  monomer designs, however they would be of greater value to a wider audience if we 
  could provide quantitative predictions of macroscopic observables such as solute 
  flux. Due to the size of the system we are studying ($\sim$62,000 atoms) it is 
  prohibitively expensive and time-consuming to run simulations longer than 
  those performed for this work ($\sim$5 $\mu$s). And even with the relatively large 
  size of our system, we only simulate 24 solute trajectories per unit cell in order
  to minimize solute-solute interactions. This results in relatively high uncertainties
  in observables such as mean squared displacement (MSD), preventing reliable long
  timescale predictions. We are in need of a way of studying the collective motion
  of a much larger set of solute over much longer timescales.

@@

  In this work, we use the output of our MD simulations to construct two new classes of 
  mathematical models which can predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. The formulation
  of these models requires a dive into stochastically driven processes.

@@

  %BJC4: added mention of the anomalous subdiffusion model we chose 
  Our first modeling approach is based on the anomalous diffusion literature, 
  applying the mathematical formalism describing subdiffusive transport to observed
  solute trajectories. Specifically, we treated our system as an FBM process subordinate
  to a CTRW, or subordinated FBM (sFBM) for short. We fit sFBM
  models in two ways: 
  %MRS4: can you clarify the sentence below? Probably something like: uses a single set of parameters in the diffusion equations, etc.
  %BJC4: see if below helps.
  %First, based on a single set of parameters. 
  First, we parameterized solute motion using a single set of parameters fit
  to a hypothesized anomalous diffusion model. Second, we used a two-state approach
  by extracting two sets of model parameters calculated based on a solute's radial
  distance from the closest pore center. We observe different dynamical behavior of
  solute within the pore region versus within the monomer tails.

@@

  Our second modeling approach applies an extended MSM framework to a relatively 
  small set of known states based on the three observed solute trapping mechanisms.  
  Standard MSMs are typically applied towards determining equilibrium populations
  of and the transitions between various state configurations.~\cite{bowman_using_2009} 
  %MRS4: this probably needs to be explained more explicitly, that the coordinates 
  %of the solute are generated according to the current state. 
  %BJC4: made more explicit.
  %We extend the framework
  %to include dynamics within states and between jumps. 
  We extend the framework to include state-dependent fluctuations and correlations in 
  solute position. 
  %MRS4: It makes sense to me what the below is, but probably isn't clear enough for others. 
  %BJC4: rephrased
%  That is we parameterize 
%  and incorporate into our model the magnitude and temporal correlation of
%  fluctuations in solute position while in each state as well as during transitions
%  to different states. 
  That is the magnitudes of a solute's fluctuations from its average trapped 
  position and the degree of correlation with its previous fluctuations is 
  defined by the parameters of its current state. To distinguish our approach from
  standard MSMs, we have named it the Markov state-dependent dynamical model (MSDDM).
  %BJC4: Added name of our modeling approach in last sentence

@@

  % BJC4: new paragraph
  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on one's research goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can then
  screen different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the anomalous diffusion model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

  %BJC4: new
  We find that the sFBM anomalous diffusion model does the best job of reproducing
  simulation behavior of all solutes studied. Therefore, we use it to demonstrate 
  how one could predict solute flux through a theoretical pore of with an 
  experimentally relevant length.

@@

  % BJC3: x --> z since I'm measuring diffusion in the z direction?
  % MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x. 
  % BJC4: I think it'll be less confusing to me writing it to change it to z.
  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, rather it follows a power law of the form:
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 0$ 
  are characteristic of Brownian and superdiffusive motion respectively.

@@

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. We can not
  observe dwell times longer than the length of a single trajectory. 
  % Could be an interesting factoid, but not necessary 
  % In fact, the longest dwell time observed by any solute in this study is X. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we may need to bound the dwell time distribution. We do this by adding 
  an exponential cut-off to the power law so the dwell time distribution is 
  now proportional to $t^{-1 - \alpha_d}e^{-\lambda t}$.
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha_d$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha_d, \lambda) = n(1 - \alpha_d)\ln\lambda - n\ln\Gamma(1 - \alpha_d, t_{min}\lambda) - \alpha_d\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This inspired two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
%  $\alpha$, $\sigma$, $H$ and, when the truncated power law is used, $\lambda$ parameters
%  fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  %MRS4: some justification on why 0.75 vs. any other cutoff.
  %BJC4: I justified sentence after next. 
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 10,000 anomalous diffusion trajectories of length
  $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
  $T_{sim}$ varied due to differing solute equilibration times. We constructed 
  trajectories by simulating sequences of dwell times and correlated hop lengths
  generated based on parameters randomly chosen from our bootstrapped parameter 
  distributions. We propagated each trajectory until the total time equaled or 
  exceeded $T_{sim}~ \mu$s, then truncated the last data point so that the total 
  time exactly equaled $T_{sim}~ \mu$s since valid comparisons are only possible 
  between fixed length sFBM simulations. 
  % BJC4: removed following sentence because I talk about aging above
  %The power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
  %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
  We reported the time-averaged MSD after time lags 40\% the length of the trajectory
  with corresponding 95\% confidence intervals.
  When simulating 2 mode models, we determined the state sequence based on random 
  draws weighted by the appropriate row of the probability transition matrix. We 
  drew hops and dwells based on the current state of the system. Since we calculated
  the transition probabilities from a finite data set, they have an associated 
  uncertainty which we 
  %MRS4: not quite sure what you mean by incorporating uncertainty. 
  %BJC4: Added comment about having a finite amount of data with which to create transition matrix. Therefore it is uncertain
  incorporated by re-sampling each row from a two dimensional Dirichlet distribution
  (also called a beta distribution for the 2D case) with concentration parameters 
  defined by the count matrix.~\cite{bacallado_bayesian_2009}

@@

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. Therefore, there is no need to 
  apply any algorithmic approaches to identify and decompose our system into 
  discrete states. The states we have chosen include all combinations of trapping
  mechanisms in the pore and out of the pore (see Table~\ref{table:states}). We use
  the same radial cut-off (0.75 nm) as in the anomalous diffusion model to differentiate
  the pore and tail region. These state choices assume that there are no significant
  kinetic effects resulting from solute conformational changes or pore size fluctuations,
  an assumption that may be relaxed in future work.

@@

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. The solutes clearly perform jumps after periods of relative
  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  anti-correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM because its analytical correlation 
  structure is close to that observed in our simulation (Figure~\ref{fig:hop_acf}). FBM
  is common in crowded viscoelastic environments where motions are highly influenced by
  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
  The parameter estimates describing our 1 and 2 mode models are summarized in 
  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} (also trying it out in 
  Figures~\ref{fig:radars} and~\ref{fig:radars_nolines})

@@

  % BJC3: is it worth trying to combine these tables?
  % BJC: note to self -- modes are flipped in simulation output because 
  % physical.partition() sets mode as booleans and when r <= 0.75, in-pore is True (1) instead of 0. 
  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol &   Methanol   & Acetic Acid  \\\hline
  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            & 0.62         & 0.45         \\\cline{2-6}
  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    & 0.44, 0.0040 & 0.08, 0.0033 \\\hline
  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            & 0.35         & 0.27         \\\cline{2-6}
  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      & 0.22, 1.80   & 0.16, 1.72   \\\hline
  Correlation   & $\gamma(H)$               & 0.37         & 0.40            & 0.30         & 0.34         \\
  \hline 
  \end{tabular}
  \caption{To create a 1 mode model for each solute, we parameterized a pure power
  law ($P(\alpha_d)$) and a truncated power law ($P_T(\alpha_d, \lambda)$) distribution 
  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
  law tails and higher values of $\lambda$ truncate the distribution at lower
  dwell times. We parameterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
  function ($\gamma(H)$) to describe the degree of correlation between hops. 
  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
  \end{table}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
  \caption{$\mathcal{N}(\sigma) / L(\sigma, \alpha_h)$}\label{fig:1mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
  \caption{$P(\alpha_d) / P_T(\alpha_d, \lambda)$}\label{fig:1mode_AD_dwells}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
  \caption{$\gamma(H)$}\label{fig:hurst_barchart}
  \end{subfigure}
  \caption{The parameters of the 1 mode model reveal differences in solute
	  dynamics. (a) We parameterized Gaussian ($\mathcal{N}(\sigma)$,
	  parameters given by bars with white background) and L\'evy stable
	  ($L(\sigma, \alpha_h)$, parameters given by bars with gray
	  background) distributions to describe solute hop lengths. We assume
	  the mean ($\mu$) to be zero for these distributions and there to be
	  no skewness ($\beta=0$) in the L\'evy stable distributions. High
	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
	  hops. (b) We parameterized a pure power law ($P(\alpha_d)$, white
	  background) and a truncated power law ($P_T(\alpha_d, \lambda)$, gray
	  background) distribution to describe solute dwell times. Lower values
	  of $\alpha_d$ lead to heavier power law tails and higher values of
	  $\lambda$ truncate the distribution at lower dwell times.(c) Finally,
	  we parameterized the hop autocorrelation function ($\gamma(H)$) to
	  describe the degree of correlation between hops.  Higher values of
	  $H$ display closer to Brownian behavior.
	  }\label{fig:1mode_bar_charts}
  \end{figure}

>>>>

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories, in order
  to predict solute mean squared displacements (MSDs). With our first model, based
  on the anomalous diffusion literature, we show how solute dynamics can be modeled as
  a fractional diffusion process subordinate to a continuous time random walk.
  We parameterize the distribution of dwell times, hop lengths between dwells and
  correlation between hops. We explore 2 variations of the model. The first variation
  applies a single set of parameters to the solutes and the second applies 2 sets
  of parameters based on the solute's radial distance from the closest pore center.
  Our second model, an adaptation of Markov state models, treats the configurational
  state of the system as a Markov process, each of which has state dependent 
  transport behavior. For each state and transition between states, we parameterized
  the distribution and temporal correlation structure of positional fluctuations as
  a means of characterization and to allow us to predict solute MSDs.
  We show that our models reasonably reproduce MSDs calculated from molecular 
  simulations. The anomalous diffusion model shows superior predictive performance, 
  in many cases reproducing MD results well within error. Finally, we
  demonstrate how one can use our models in order to calculate the mean
  first passage time, a quantity related to solute flux, of a given
  solute across a macroscopic-length pore. Overall this work makes
  great strides towards understanding the relationship between
  microscopic chemically-dependent solute motions and macroscopic membrane performance.

  %Overall, this work the parameters of each model to identify specific differences
  %in solute
  %transport behavior which can help suggest modifications that can be
  %made to LLC membrane monomers in order to increase or reduce
  %selectivity towards a specific solute or class of solutes.

@@

  Mathematical descriptions of transport in complex separations membranes are 
  a powerful way to understand mechanisms and formulate membrane design principles. 
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  The complexity of a model generally parallels the complexity of the transport 
  mechanism at hand, as well as the transport information the model conveys.
  In dense homogeneous membranes, the solution-diffusion model can extract 
  diffusion and partition coefficients and has successfully predicted solute 
  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
  models yield predictions of diffusion coefficients and solute transport rates 
  in nanoporous membranes.~\cite{paul_diffusive_1974} More recently, single particle 
  tracking approaches have taken us beyond continuum modeling and allow us to 
  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
  level, one can use molecular dynamics (MD) simulations to study both single 
  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
  All of these approaches facilitate speculation on the molecular origins of separations
  by attempting to give a more intuitive understanding of how solutes move as a function
  of their environment, in turn suggesting experiments that could be performed.

@@

  %BJC4: Added next two paragraphs to help ease more into time series modeling
  So far, our molecular models have provided valuable qualitative mechanistic insight 
  with some quantitative support which already allows us to speculate about new LLC
  monomer designs, however they would be of greater value to a wider audience if we 
  could provide quantitative predictions of macroscopic observables such as solute 
  flux. Due to the size of the system we are studying ($\sim$62,000 atoms) it is 
  prohibitively expensive and time-consuming to run simulations longer than 
  those performed for this work ($\sim$5 $\mu$s). And even with the relatively large 
  size of our system, we only simulate 24 solute trajectories per unit cell in order
  to minimize solute-solute interactions. This results in relatively high uncertainties
  in observables such as mean squared displacement (MSD), preventing reliable long
  timescale predictions. We are in need of a way of studying the collective motion
  of a much larger set of solutes over much longer timescales.

@@

  In this work, we use the output of our MD simulations to construct two classes of 
  mathematical models which can predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. The formulation
  of these models requires a dive into stochastically driven processes.

@@

  %BJC4: added mention of the anomalous subdiffusion model we chose 
  Our first modeling approach is based on the anomalous diffusion (AD) literature, 
  applying the mathematical formalism describing subdiffusive transport to observed
  solute trajectories. Specifically, we treated our system as an FBM process subordinate
  to a CTRW, or subordinated FBM (sFBM) for short. We fit sFBM
  models in two ways: 
  %MRS4: can you clarify the sentence below? Probably something like: uses a single set of parameters in the diffusion equations, etc.
  %BJC4: see if below helps.
  %First, based on a single set of parameters. 
  First, we parameterized solute motion using a single set of parameters fit
  to a hypothesized AD model. Second, we used a two-state approach
  by extracting two sets of model parameters calculated based on a solute's radial
  distance from the closest pore center. We observe different dynamical behavior of
  solute within the pore region versus within the monomer tails.

@@

  Our second modeling approach applies an extended MSM framework to a relatively 
  small set of known states based on the three observed solute trapping mechanisms.  
  Standard MSMs are typically applied towards determining equilibrium populations
  of and the transitions between various state configurations.~\cite{bowman_using_2009} 
  %MRS4: this probably needs to be explained more explicitly, that the coordinates 
  %of the solute are generated according to the current state. 
  %BJC4: made more explicit.
  %We extend the framework
  %to include dynamics within states and between jumps. 
  We extend the framework to include state-dependent fluctuations and correlations in 
  solute position. 
  %MRS4: It makes sense to me what the below is, but probably isn't clear enough for others. 
  %BJC4: rephrased
%  That is we parameterize 
%  and incorporate into our model the magnitude and temporal correlation of
%  fluctuations in solute position while in each state as well as during transitions
%  to different states. 
  That is, the magnitudes of a solute's fluctuations from its average trapped 
  position and the degree of correlation with its previous fluctuations is 
  defined by the parameters of its current state. To distinguish our approach from
  standard MSMs, we have named it the Markov state-dependent dynamical model (MSDDM).
  %BJC4: Added name of our modeling approach in last sentence

@@

  % BJC4: new paragraph
  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on one's research goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can then
  screen different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the AD model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

  %BJC4: new
  We find that the AD model does the best job of reproducing
  simulation behavior of all solutes studied. Therefore, we use it to
  demonstrate how one could predict the mean first passage time (MFPT) through
  a theoretical pore with an experimentally relevant length. We show that the
  MFPT grows super-linearly with pore length and that the associated growth
  exponent increases as solute motion becomes more anti-correlated

@@

  % BJC3: x --> z since I'm measuring diffusion in the z direction?
  % MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x. 
  % BJC4: I think it'll be less confusing to me writing it to change it to z.
  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, rather it follows a power law of the form:
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate the MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 1$ 
  are characteristic of Brownian and superdiffusive motion respectively.

@@

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. We can not
  observe dwell times longer than the length of a single trajectory. 
  % Could be an interesting factoid, but not necessary 
  % In fact, the longest dwell time observed by any solute in this study is X. 
  In order to directly compare our AD model to finite-length MD 
  trajectories we may need to bound the dwell time distribution. We do this by adding 
  an exponential cut-off to the power law so the dwell time distribution is 
  now proportional to $t^{-1 - \alpha_d}e^{-\lambda t}$.
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha_d$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha_d, \lambda) = n(1 - \alpha_d)\ln\lambda - n\ln\Gamma(1 - \alpha_d, t_{min}\lambda) - \alpha_d\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This inspired two AD 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
%  $\alpha$, $\sigma$, $H$ and, when the truncated power law is used, $\lambda$ parameters
%  fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  %MRS4: some justification on why 0.75 vs. any other cutoff.
  %BJC4: I justified sentence after next. 
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 10,000 AD trajectories of length
  $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
  $T_{sim}$ varied due to differing solute equilibration times. We constructed 
  trajectories by simulating sequences of dwell times and correlated hop lengths
  generated based on parameters randomly chosen from our bootstrapped parameter 
  distributions. We propagated each trajectory until the total time equaled or 
  exceeded $T_{sim}~ \mu$s, then truncated the last data point so that the total 
  time exactly equaled $T_{sim}~ \mu$s since valid comparisons are only possible 
  between fixed length sFBM simulations. 
  % BJC4: removed following sentence because I talk about aging above
  %The power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
  %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
  We reported the time-averaged MSD up to 1000 ns time lags with corresponding
  95\% confidence intervals.  When simulating 2 mode models, we determined the
  state sequence based on random draws weighted by the appropriate row of the
  probability transition matrix. We drew hops and dwells based on the current
  state of the system. Since we calculated the transition probabilities from a
  finite data set, they have an associated uncertainty which we 
  %MRS4: not quite sure what you mean by incorporating uncertainty. 
  %BJC4: Added comment about having a finite amount of data with which to create transition matrix. Therefore it is uncertain
  incorporated by re-sampling each row from a two dimensional Dirichlet distribution
  (also called a beta distribution for the 2D case) with concentration parameters 
  defined by the count matrix.~\cite{bacallado_bayesian_2009}

@@

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. Therefore, there is no need to 
  apply any algorithmic approaches to identify and decompose our system into 
  discrete states. The states we have chosen include all combinations of trapping
  mechanisms in the pore and out of the pore (see Table~\ref{table:states}). We use
  the same radial cut-off (0.75 nm) as in the AD model to differentiate
  the pore and tail region. These state choices assume that there are no significant
  kinetic effects resulting from solute conformational changes or pore size fluctuations,
  an assumption that may be relaxed in future work.

@@

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. The solutes clearly perform jumps after periods of relative
  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  anti-correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM because its analytical correlation 
  structure is close to that observed in our simulation (Figure~\ref{fig:hop_acf}). FBM
  is common in crowded viscoelastic environments where motions are highly influenced by
  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
  The parameter estimates describing our 1 and 2 mode models are summarized in 
  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} (also trying it out in 
  Figures~\ref{fig:radars},~\ref{fig:radars_nolines},~\ref{fig:1mode_bar_charts}, and~\ref{fig:2mode_bar_charts})

@@

  % BJC3: is it worth trying to combine these tables?
  % BJC: note to self -- modes are flipped in simulation output because 
  % physical.partition() sets mode as booleans and when r <= 0.75, in-pore is True (1) instead of 0.
  %BJC4: will likely move these tables to supporting.
  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol &   Methanol   & Acetic Acid  \\\hline
  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            & 0.62         & 0.45         \\\cline{2-6}
  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    & 0.44, 0.0040 & 0.08, 0.0033 \\\hline
  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            & 0.35         & 0.27         \\\cline{2-6}
  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      & 0.22, 1.80   & 0.16, 1.72   \\\hline
  Correlation   & $\gamma(H)$               & 0.37         & 0.40            & 0.30         & 0.34         \\
  \hline 
  \end{tabular}
  \caption{To create a 1 mode model for each solute, we parameterized a pure power
  law ($P(\alpha_d)$) and a truncated power law ($P_T(\alpha_d, \lambda)$) distribution 
  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
  law tails and higher values of $\lambda$ truncate the distribution at lower
  dwell times. We parameterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
  function ($\gamma(H)$) to describe the degree of correlation between hops. 
  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
  \end{table}

@@

  %BJC4: I think these next two figures are the way to go.
  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
  \caption{$\mathcal{N}(\sigma) / L(\sigma, \alpha_h)$}\label{fig:1mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
  \caption{$P(\alpha_d) / P_T(\alpha_d, \lambda)$}\label{fig:1mode_AD_dwells}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
  \caption{$\gamma(H)$}\label{fig:hurst_barchart}
  \end{subfigure}
  \caption{The parameters of the 1 mode model reveal differences in solute
	  dynamics. (a) We parameterized Gaussian ($\mathcal{N}(\sigma)$,
	  parameters given by bars with white background) and L\'evy stable
	  ($L(\sigma, \alpha_h)$, parameters given by bars with gray
	  background) distributions to describe solute hop lengths. We assume
	  the mean ($\mu$) to be zero for these distributions and there to be
	  no skewness ($\beta=0$) in the L\'evy stable distributions. High
	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
	  hops. (b) We parameterized a pure power law ($P(\alpha_d)$, white
	  background) and a truncated power law ($P_T(\alpha_d, \lambda)$, gray
	  background) distribution to describe solute dwell times. Lower values
	  of $\alpha_d$ lead to heavier power law tails and higher values of
	  $\lambda$ truncate the distribution at lower dwell times.(c) Finally,
	  we parameterized the hop autocorrelation function ($\gamma(H)$) to
	  describe the degree of correlation between hops.  Higher values of
	  $H$ display closer to Brownian behavior.
	  }\label{fig:1mode_bar_charts}
  \end{figure}
